---
title: "G&S_311"
author: "Yu Du"
date: "2/9/2021"
output: pdf_document
---

In the textbook, on Page 102:
•	null hypothesis is p=0.6 and the alternate hypothesis is p>0.6
•	n=100 (the number of people we give aspirin to take) and we need to select m (the critical value for our experiment, we reject the null hypothesis if at least m people are cured, and otherwise we accept it) to make both type 1 error and type 2 error as small as possible.
```{r}
#dbinom(x,n,p)

#Create PowerCurve.
#p ranging from 0.4 to 1.

#First create the probability function alpha.
alpha<-function(k){
  p<-seq(0.4,1,1/100)
  binom<-dbinom(k,100,p)
  result<-cumsum(binom)
  return(result)
}
```

```{r}
#alpha(60)
#alpha(80)
```


```{r}
#Create PowerCurve.
library(ggplot2)

PowerCurve<-function(m1,m2){
  p<-seq(0.4,1,1/100)
  power1<-alpha(m1)
  power2<-alpha(m2)
ggplot()+geom_line(aes(p,power1),color="peru")+geom_line(aes(p,power2),color="blue")+geom_rect(aes(xmin=0.6,xmax=0.8,ymin=0.05,ymax=0.95),color="black",alpha=0)+xlab("Probability")+ylab("Power")+
  ggtitle("The Power Curve") +theme_classic()+
  theme(plot.title = element_text(hjust = 0.5))
}
```


We need to find values of m between 60 and 80 to make the graphs of $\alpha$ enter the box from .6 to .8, with bottom and top at heights .05 and .95.
we first take a look on the graphs of alpha in the plot when m1=60 and m2=80.
```{r}
PowerCurve(60,80)
```

Now, changing m1 to 65 shows that the graph of $\alpha$ moves to right as m increases. 
```{r}
#change m1 to 65.
PowerCurve(65,80)
```

We need to increase m1 and decrease m2 to make the graphs of $\alpha$ enter the box. After taking several tries, we find that m1=69 and m2=73. Below are some examples for increasing m1 and decreasing m2.
```{r}
PowerCurve(67,76)
```
```{r}
PowerCurve(68,74)
```


As the plot shown below, when m1=69 and m2=73, the graphs of $/alpha$ enter the box. This plot is same as figure 3.7 in the textbook. m1=69 is the smallest value for m that thwarts a type 1 error, while m = 73 is the largest which thwarts a type 2. Therefore, we need take the critical value m for our experiment between 69 and 73.
```{r}
PowerCurve(69,73)
```

